---
title: "Exploratory Data Analytics corsework"
author: "K.TAKAKI"
date: "2022/1/24"
output: 
        html_document: 
                keep_md: yes

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
```

## download and unzip the file

```{r, cache=TRUE}
path <- getwd()
url <- "https://d396qusza40orc.cloudfront.net/exdata%2Fdata%2FNEI_data.zip"
download.file(url, file.path(path, "exdata_data_NEI_data.zip"))
unzip("exdata_data_NEI_data.zip")
NEI <- readRDS("summarySCC_PM25.rds")
SCC <- readRDS("Source_Classification_Code.rds")
```

## 


```{r, cache=TRUE}
head(NEI)
head(SCC)
```

# total emissions from PM2.5 decreased in the United States from 1999 to 2008
Let's make a plot showing the total PM2.5 emission from all sources for each of the years 1999, 2002, 2005, and 2008 using base plot system.
```{r, cache=TRUE}
merged_data <- merge(NEI, SCC, by = "SCC")
anual_total_emission <- aggregate(Emissions ~ year, data = merged_data, sum, na.rm=TRUE)
g1 <-barplot(height = anual_total_emission$Emissions, names = anual_total_emission$year, main = "Total emissions from PM2.5 in the United States from 1999 to 2008", ylab = "Total Emissions")
dev.off()
```

# total emissions from PM2.5 decreased in the Baltimore City, Maryland (fips == "24510"|}fips == "24510") from 1999 to 2008?

```{r, cache=TRUE}
baltimore_type <- aggregate(Emissions ~ year + type, data = subset(merged_data, fips == "24510"), sum, na.rm=TRUE)
baltimore_data <- aggregate(Emissions ~ year, data = subset(merged_data, fips == "24510"), sum, na.rm=TRUE)
g2 <- barplot(height = baltimore_data$Emissions, names = baltimore_data$year, main = " Total emissions from PM2.5 in the Baltimore City, Maryland from 1999 to 2008", ylab = "Total Emissions")
```

```{r, cache=TRUE}
g3 <- ggplot(baltimore_type, aes(year, Emissions, color = type)) + geom_line(aes(fill=type), show.legend = TRUE)
g3 <- g3 + labs(title = "Four sources of emissions from 1999–2008 for Baltimore City",
                x = "year")
g3
```

check which column contains "coal"
```{r, cache=TRUE}
length(grep("[Cc]oal", SCC$Short.Name))
length(grep("[Cc]oal", SCC$SCC.Level.One))
length(grep("[Cc]oal", SCC$SCC.Level.Two))
length(grep("[Cc]oal", SCC$SCC.Level.Three))
length(grep("[Cc]oal", SCC$SCC.Level.Four))
```


```{r, cache=TRUE}
coal_list <- grep("[Cc]oal", merged_data$Short.Name)
coal_list <- append(coal_list ,grep("[Cc]oal", merged_data$SCC.Level.Three))
coal_list <- append(coal_list ,grep("[Cc]oal", merged_data$SCC.Level.Four))
coal_list <- unique(coal_list)
coal_related_emission <- aggregate(Emissions ~ year, data = merged_data[coal_list,4:6], sum, na.rm=TRUE)
g4 <- ggplot(coal_related_emission, aes(factor(year), Emissions, fill=Emissions)) + geom_bar(stat = "identity")
g4 <- g4 + labs(title = "Total emissions from coal combustion-related sources",x = "year")
```


we only need to change the "fips" for emissions from motor vehicle source
```{r, cache=TRUE}
vehicle <- function(index) {
        car_data <- subset(merged_data, fips == index)
        col_list <- NULL
        for (i in 1: ncol(car_data))
                if (length(grep("[Cc]ar", car_data[,i])) > 0) {col_list <- append(col_list, i);
                print(colnames(car_data[i]))}
        data_list <- NULL
        for (i in 1 : length(col_list)) col_list <- append(col_list, grep("[Cc]ar", car_data[,col_list[i]]))
        data_list <- unique(data_list)
        car_related_emission <- aggregate(Emissions ~ year, data = car_data[col_list, 4:6], sum, na.rm=TRUE)
        g <- ggplot(car_related_emission, aes(factor(year), Emissions, fill=Emissions)) + geom_bar(stat = "identity")
        g
}
```

```{r, cache=TRUE}
g5 <- vehicle("24510")
g5 <- g5 + labs(title = "Emissions from motor vehicle sources changed in Baltimore City",x = "year")
g5
```

```{r, cache=TRUE}
compare_car <- function(index) {
        car_data <- subset(merged_data, fips == index)
        col_list <- NULL
        for (i in 1: ncol(car_data))
                if (length(grep("[Cc]ar", car_data[,i])) > 0) {col_list <- append(col_list, i);
                print(colnames(car_data[i]))}
        data_list <- NULL
        for (i in 1 : length(col_list)) col_list <- append(col_list, grep("[Cc]ar", car_data[,col_list[i]]))
        data_list <- unique(data_list)
        car_related_emission <- aggregate(Emissions ~ year, data = car_data[col_list, 4:6], sum, na.rm=TRUE)
}
bal_car <- compare_car("24510")
LA_car <- compare_car("06037")
bal_car <- mutate(bal_car, country = "baltimore")
LA_car <- mutate(LA_car, country = "Los Angels")
t <- rbind(bal_car, LA_car)
g6 <- ggplot(t, aes(factor(year), Emissions, fill = country, color = country)) + geom_bar(stat = "identity", show.legend = TRUE, position = "dodge")
g6 <- g6 + labs(title = "Emissions from motor souces in Baltimore city and LA", x = "year")
g6
```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
